DraftFunctions

### 2021-05-10 R/DraftFunctions.Rmd
Global options (zzz file)

```{r}
library(dplyr)
library(tibble)
library(tidyr)
```

```{r}
ParamCrownDiameterAllometry <- read_delim("D:/VSC Kourou/DATA/ParamCrownDiameterAllometry.csv", 
    ";", escape_double = FALSE, col_types = cols(alpha = col_number(), 
        beta = col_number()), locale = locale(decimal_mark = ","), 
    trim_ws = TRUE) %>%
  separate(ScientificName, sep = "_", into = c("Genus", "Species"), remove = F) %>% 
  mutate(Family = ifelse(Taxo == "fam", Genus, NA)) %>% 
  mutate(Genus = ifelse(is.na(Family), Genus, NA))

@@

@@

@@

if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH doesn't exist create it
   Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it

@@

# TreeHarvestableVolume
  left_join(ForestZoneVolumeParametersTable) %>% 
  mutate(TreeHarvestableVolume = aCoef + bCoef * CircCorr^2) %>%  # compute the tree harvestable volume

# TrunkHeight & CrownHeight  
  mutate(TrunkHeight = TreeHarvestableVolume/(pi*(DBH/2)^2)) %>%  # compute the trunk height (cylinderVolume= π(DBH/2)² x H)
  # mutate(CrownHeight = TreeHeight - TrunkHeight) %>%  # compute the crown height TREEHEIGHT EN ATTENTE

# CrownDiameter
  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
  left_join(spParamCrownDiameter, by = c("ScientificName","Genus","Species")) %>% #Add parameters at species scale
  left_join(genParamCrownDiameter, by = "Genus", suffix = c(".species", ".genus")) %>% #Add parameters at genus scale
  left_join(famParamCrownDiameter, by = "Family") %>% #Add parameters at family scale

@@

  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-Taxo.species, -Taxo.genus, -Taxo.family) %>%  #remove obsolete columns
  # mutate(CrownDiameter = exp((
  # (ln(DBH)-alpha-error)/beta)
  # )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries))

>>>>

```{r}
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
```

```{r ParamCrownDiameterAllometry table code}
ParamCrownDiameterAllometry <- read_delim("D:/VSC Kourou/DATA/ParamCrownDiameterAllometry.csv", 
    ";", escape_double = FALSE, col_types = cols(alpha = col_number(), 
        beta = col_number()), locale = locale(decimal_mark = ","), 
    trim_ws = TRUE) %>%
  separate(ScientificName, sep = "_", into = c("Genus", "Species"), remove = F) %>% 
  mutate(Family = ifelse(Taxo == "fam", Genus, NA)) %>% 
  mutate(Genus = ifelse(is.na(Family), Genus, NA))

@@

```{r SpeciesCriteria table code}
SpeciesCriteria <- read_delim("D:/VSC Kourou/DATA/SpeciesCriteria.csv", 
    ";", escape_double = FALSE, col_types = cols(Commercial = col_factor(levels = c("1", 
        "2")), MinFD = col_number(), UpMinFD = col_number(), 
        MaxFD = col_number()), locale = locale(encoding = "Latin1"), 
    trim_ws = TRUE) %>% 
  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T) %>% 
  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)

usethis::use_data(SpeciesCriteria)
```

@@

# My custom options
faut ptetre mettre Maria. devant  chaque objet!
```{r}
# Mimimum DBH value = 10 cm
# Maximum area slope = 27%
# Maximum main&2nd trail centerline slope = 22%
# Maximum main&2nd trail cross slope = 4%
# Grapple maximum slope = 20%
# Trees slope = 22%
# Plateau maximum slope = 5%
# Distance to compute slope = 6 m (3m for each side)
# water sources buffer zone = 30 m
# Main trail width = 5-6 m
# 2nd trail width = 4 m
# Big trees = 50 cm
# Objective bonus = 20-30%
# Cable = 40 m
# Grapple = 6 m
# Isolate tree minimum distance = 100 m
# Future trees minimum diameter = 35 cm
# TreefallSuccess proportion = 0.6
# Treefall orientation = 30-45◦
# (Hollow) Part taken from hollow trees for fuel exploitation = 1/3
# Purge = 0.14
# Maximum TrailDensity = 200 m/ha
# Maximum landing area = 1 500 m^2

# TrunkHeight formule : TrunkHeight = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2))
# CrownDiameter formule : CrownDiameter = exp(((ln(DBH)-alpha-error)/beta))/TreeHeight
# RottenModel

pars <- list(MinDBHValue = 10, #in cm
  MaxAreaSlope = 27, #in %
  MaxTrailCenterlineSlope = 22, #in %
  MaxTrailCrossSlope = 4, #in %
  GrappleMaxslope = 20, #in %
  TreeMaxSlope = 22, #in %
  PlateauMaxSlope = 5, #in %
  SlopeDistance = 6, #in m (3m for each side)
  WaterSourcesBufferZone = 30, #in m
  MainTrailWidth = 5-6, #in m
  "2ndTrailWidth" = 4, #in m
  BigTrees = 50, #in cm
  ObjectiveBonus = 20-30, #in % (ObjectiveBonus >= 20 && ObjectiveBonus =< 30 ou c(20:30))
  CableLength = 40, #in m
  GrappleLength = 6, #in m
  IsolateTreeMinDistance = 100, #in m
  FutureTreesMinDiameter = 35, #in cm
  TreefallSuccessProportion = 0.6,
  TreefallOrientation = 30-45, #in degree (◦)
  TreeHollowPartForFuel = 1/3, #(Hollow) Part taken from hollow trees for fuel exploitation
  Purge = 0.14, # in m^3 of fuelwood/m^3 of logged trees  
  MaxTrailDensity = 200, #in m/ha
  MaxLandingArea = 1500, #in square meters
  TrunkHeightAllometry = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2)),
CrownDiameterAllometry = exp(((ln(DBH)-alpha-error)/beta))/TreeHeight,
RottenModel = ) 
```

@@

if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH (cm) doesn't exist create it
   Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it

@@

# TreeHarvestableVolume (m^3)
  left_join(ForestZoneVolumeParametersTable) %>% 
  mutate(TreeHarvestableVolume = aCoef + bCoef * (DBH/100)^2) %>%  # compute the tree harvestable volume

# TrunkHeight & CrownHeight (m)
  mutate(TrunkHeight = TreeHarvestableVolume/(pi*(((DBH/100)/2)^2))) %>%  # compute the trunk height (cylinderVolume= π(DBH/2)² x H) DBH in cm, in m in the formule.
  # mutate(CrownHeight = TreeHeight - TrunkHeight) %>%  # compute the crown height TREEHEIGHT EN ATTENTE

# CrownDiameter (m)
  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
  left_join(spParamCrownDiameter, by = c("ScientificName","Genus","Species")) %>% #Add parameters at species scale
  left_join(genParamCrownDiameter, by = "Genus", suffix = c(".species", ".genus")) %>% #Add parameters at genus scale
  left_join(famParamCrownDiameter, by = "Family") %>% #Add parameters at family scale

@@

  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-Taxo.species, -Taxo.genus, -Taxo.family) #remove obsolete columns
  # mutate(CrownDiameter = exp((
  # (ln(DBH)-alpha-error)/beta)
  # )/TreeHeight) # compute the crown diameter (CD) (ln(D) = 𝜶+ 𝜷 ln(H*CD) + 𝜺, with 𝜺~N(0,σ^2) and meanσ^2 = 0.0295966977. (Mélaine's allometries))
